\documentclass{beamer}

\begin{document}

\begin{frame}{Scholarly Report - Publications}
Published:
\begin{itemize}
  \item Journal - 27 refereed journal papers (7 since receiving tenure in 2006)
  \item Peer Reviewed Conference - 48 peer reviewed conference papers (32 since tenure, 
  	of which 22 were on research and 10 were on education)
  \item Book chapters - 2 (all since tenure)
  \item Industrial reports - 6  (all since tenure)
  \item US patents - 2 (second author, since tenure)
\end{itemize}
Under Review:
\begin{itemize}
  \item One paper submitted to ACS Omega
  \item One paper submiteed to Experimental Thermal and Fluid Science
\end{itemize}
\end{frame}

\begin{frame}{Scholarly Report - Journal Papers since tenure}
Authorship: 
\begin{itemize}
  \item Sole author on one journal paper, 
  \item Second author on four papers, 
  \item Co-author on two papers 
\end{itemize}

Venues: 
\begin{itemize}
  \item One paper in 2007 as sole author in Experimental Thermal and Fluid Science,
  \item  Five papers in  fully open access MDPI journals: Energies (3 papers), 
  	Thermo (1 paper), and Processes (1 paper) 
  \item One paper in  open access journal through the American Chemical Society, ACS Omega. 
\end{itemize}
\end{frame}

\begin{frame}{Scholarly Report - Presentations, Lab Development and Citations}
Conference Presentations:
\begin{itemize}
  \item Total - 36
  \item Post-teunre - 20 (15 on research and 5 on education)
\end{itemize}

Lab Development: 
\begin{itemize}
  \item Equipment purchased using DOE grant during 2009-2011
\end{itemize}

Citation: 
\begin{itemize}
  \item Google 622 (including self-citations)
  \item Scopus 493 (408 excluding without self-citations)
\end{itemize}

\end{frame}

\begin{frame}{Scholarly Report - Grants and Contracts} 
The scholarly report has a table with details. 
Some projects have no or incomplete backup information at the time of the scholarly report being authored. 
\begin{itemize}
  \item PI - \$522,900 (\$200,000 as a takeover PI) 
  \item Co-PI - \$762,023
  \item SP - \$416,598
\end{itemize}
\end{frame}

\begin{frame}{Scholarly Report - Dissertation and Thesis Supervision}
\begin{itemize}
  \item Graduated two Ph.D. students (one since tenure)
  \item Advising one Ph.D. dissertion in progress
  \item Advised one Ph.D. student who droped
  \item Member of 22 SECS Ph.D. dissertation committees
  \item Member of 5 Master's thesis committees  
\end{itemize} 
\end{frame}

\begin{frame}{Scholarly Report - External Reviews} 
A total of 19 reviews were solicitated (6 provided by candidate and 13 by scholarly committee) and 5 were received. 

\vspace{\fill}

Most of letters commented positively on the quality and impact of Dr. Kobus’ earlier publications, on his educational efforts and on his high level of involvement in the ASME and ASTEF professional societies. Several noted a low number of graduate student supervision and others commented on the lower quality/impact of his recent publication venues, but then also went on to highlight the value and impact of his educational and service contributions.

\end{frame}

\begin{frame}{Teaching Report}
\begin{itemize}
  \item Taught 22 courses with Q12 ranges between 3.3 and 5 for undergradaute courses and between 3.5 and 5 for graduate courses. 
  \item Developed or enchanced 6 courses
  \item Upgraded and added numerous lab materials
  \item Supervised 19 undergraduate ME 490 Student Projects 
  \item Supervised 3 Honors College theses
  \item Supervised 3 groups of teachers in NSF-RET program
  \item Supervised high school students
  \item Chaired DAC’s of two Ph.D. graduates
  \item Chaired DAC of one Ph.D. student who dropped
  \item Chairing one DAC. 
  \item Member of about 20 DACs
  \item Member of 5 master thesis committees.
  \item Supervised two ME 690 graduate student projects prior to tenure   
\end{itemize}

\end{frame}

\begin{frame}{Teaching Report - Funding}
Dr. Kobus has been active in seeking funding for his teaching/outreach activities as SECS director of Outreach, Recruitment and Retention. Since promotion to Associate Professor, he has obtained 89 external educational grants as PI totaling \$4,009,705 
(\$1,978,337 in OU matching funds), 6 external grants as co-PI totaling \$1,043,969.50 (\$45,000 in OU matching funds) 
and 4 external grants as senior personnel totaling \$577,598. 
Funding sources include: US Department of Energy, Army Educational Outreach Program, 
Pontiac Public Schools, Michigan Initiative for Innovation and Entrepreneurship, 
National Science Foundation, NASA Space Grant Consortium, ESG Engineering, FCA Automobiles, General Dynamics Land Systems, Michigan Woman’s Foundation, Ford Motor Company, Michigan Talent Investment Agency.
\end{frame}

\begin{frame}{Teaching Report - Conference Papers}
Published a total of 16 educational conference papers. 
\begin{itemize}
  \item 9 as Firt author (6 since tenure)
  \item 7 as Co-authoer (3 since tenure
\end{itemize}

\end{frame}

\begin{frame}{Teaching Report - Awards} 
\begin{itemize}
  \item Oakland University Teaching Excellence Award, 2019. 
  \item SECS Outstanding Faculty Award for Teaching, 2014.
  \item Dr. Wilbert J. McKeachie International Poster Prize for the best poster at the 2013 OU-Windsor 7th Annual Conference on Teaching and Learning 
  \item Recognition for Teaching, Oakland University Founder’s Day, 2012
\end{itemize}

\end{frame}

\begin{frame}{Teaching Report - Peer Perception}
Dr. Barber visited EGR 2905 twice and reported that
\begin{itemize}
  \item The lectures began on time
  \item  Dr. Kobus explained the course material in detail and with great enthusiasm
  \item Dr. Kobus frequently stopped the lecture and asked questions or asked the students if they had questions
  \item  Students responded to all questions asked and sometimes asked their own questions
  \item  Dr. Kobus seemed to enhance student interest in the course material
  \item  Dr. Kobus records all lectures to allow students to review the lecture material outside of class.
\end{itemize}
\end{frame}

\begin{frame}{Teaching Report - Student Perception}
Teaching Committee's Findings based on four charts: 
\begin{itemize}
  \item  (1) Ratings each Semester in Comparison with All SECS Faculty -  For the 30 semesters shown in the chart, Dr. Kobus scored below average 12 times and above average 13 times
  \item (2) Ratings by Course Levels - Dr. Kobus’s scores stand above or equal to the averages of all levels 
  \item (3) Ratings by Instructor’s Rank -  the scores received by Dr. Kobus were below the averages 13 times and above average 14 times over the total 30 semesters
  \item (4) Ratings by Course Enrollments - Dr. Kobus’s rating is above the average of all class sizes
\end{itemize}

\end{frame}

\begin{frame}{Teaching Report - Student Perception}
End-of-Semester Comments: Most students of Dr. Kobus were very pleased with his teaching while a handful of students thought otherwise
\vspace{\fill}

Student letters:
A total of letters were received. Based on quoted remarks, 7 students are positive and 1 is ambivalent. 
\end{frame}

\begin{frame}{Service Report}

\end{frame}

\begin{frame}{Service Report}

\end{frame}

\begin{frame}{Service Report}

\end{frame}

\begin{frame}{Service Report}

\end{frame}

\begin{frame}{Service Report}

\end{frame}

\end{document}